Mainstreaming Race Science

### 2023-06-22 paper/paper.Rmd
paper stuff

@@

## Data preparation

@@

### Vocabulary selection

>>>>

*[for xref: https://bookdown.org/yihui/bookdown/a-single-document.html]*

@@

## Text preparation

@@

### Data and code availability

Document metadata retrieved from Crossref does not appear to be covered by any copyright or other intellectual property restrictions.  However, due to copyright restrictions, we are unable to make document fulltext or Web of Science search results publicly available.  Code for the corpus assembly and text preparation steps described above is available by request.

The public analysis repository, <https://github.com/dhicks/race-science> *[DOI]*, includes document metadata and documentwise counts of NLP-extracted noun phrases ("document-term matrices"), along with code to reproduce the analysis of the following sections.  *[repo readme: requires R 4.1.2; rig (<https://github.com/r-lib/rig/>) for managing multiple R installations]*

## Vocabulary selection
